Benchmarking on Rigetti architecture

### 2022-11-07 txt/manuscript.tex
changing drawings
add mathematical foundations

\todo[inline]{wyzej mamy bez daggera, trzeba to ustalic} 
%\begin{figure}[h!]
%	\includegraphics[scale=1.5]{onequbit.pdf}
%	\caption{A schematic representation of the setup for distinguishing
%		measurements using postselection.}
%	\label{postselection}
%\end{figure}

@@

The celebrated result by Helstrom~\cite{helstrom1976quantum} gives the optimal  probability of correct discrimination between two quantum operations, $\TT$  and $\SS$, 
in terms of their distance with the use of the diamond norm
\begin{equation}
p_{\text{succ}}(\TT, \SS) =  \frac12 + \frac14 \| \TT - \SS \|_\diamond.
\end{equation}
In the case of discrimination between two von Neumann measurements $\PP_U$ and 
$\PP_\Id$ we know that (from Theorem 1 \cite{puchala2018strategies})
\begin{equation}
\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
\Phi_\Id\|_\diamond,
\end{equation}
where $\Phi_U$ is unitary channel and $\diaguni_d$ be the set of diagonal 
unitary matrices of dimension $d$.

>>>>

%\begin{figure}[h!]
%	\includegraphics[scale=1.5]{onequbit.pdf}
%	\caption{A schematic representation of the setup for distinguishing
%		measurements using postselection.}
%	\label{postselection}
%\end{figure}

@@

The celebrated result by Helstrom~\cite{helstrom1976quantum} gives the optimal  probability of correct discrimination between two quantum operations, $\TT$  and $\SS$, 
in terms of their distance with the use of the diamond norm
\begin{equation}
p_{\text{succ}}(\TT, \SS) =  \frac12 + \frac14 \| \TT - \SS \|_\diamond.
\end{equation}
In the case of discrimination between two von Neumann measurements $\PP_U$ and 
$\PP_\Id$ we know that (from Theorem 1 in \cite{puchala2018strategies})
\begin{equation}
\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
\Phi_\Id\|_\diamond,
\end{equation}
where $\Phi_U$ is unitary channel and $\diaguni_d$ be the set of diagonal 
unitary matrices of dimension $d$.
